Joint analysis of read count data

### 2020-09-11 combined_analysis/combine_all_DLPFC.Rmd
Inital commit

  res = lapply(coefTest, function(coef){
    res1 = run_zenith( fit, coef, gs.GO.collection )
    res1$Resource = 'GO'

    res2 = run_zenith( fit, coef, gs.MSigDB.collection )
    res2$Resource = "MSigDB"

    res = rbind(res1, res2)
    res$Coef = coef
    res$Cohort = key

    res
  })
  do.call(rbind, res)
})
names(res_zenith) = names(fit_marginal.lst)
```

>>>>

  res.GO = run_zenith( fit, coefTest, gs.GO.collection )
  res.GO$Resource = "GO"
  res.GO$Cohort = key

  res.MSigDB = run_zenith( fit, coefTest, gs.MSigDB.collection )
  res.MSigDB$Resource = "MSigDB"
  res.MSigDB$Cohort = key

  rbind(res.GO, res.MSigDB)

})
names(res_zenith) = names(fit_marginal.lst)
```
